% project checkoff checklist

\documentclass{article}

\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{amssymb}

\title{6.111 Final Project\\Project Checklist}
\date{21 November 2011}
\author{Logan P. Williams\\Jos\'{e} E. Cruz Serrall\'{e}s}

\renewcommand{\labelitemii}{$\Box$}

\begin{document}
\maketitle

\begin{itemize}
% Logan
\item[] {\tt projective\_transform}
	\begin{itemize}
	\item 1
	\item 2
	\item etc
	\end{itemize}

% Logan
\item[] {\tt object\_recognition}
	\begin{itemize}
	\item 1
	\item 2
	\item etc
	\end{itemize}

% Jose
\item[] {\tt memory\_interface}: efficiently interfaces with the memory and all of the modules that have to write to and read from ZBT memory.
	\begin{itemize}
	\item Writes data element two cycles after pulsing ``done" to module.
	\item Reads data element and outputs two cycles after pulsing ``done" to module.
	\item Correctly parses relative $(x,y)$ coordinates, based on the module that is requesting a memory access and the location of its image.
	\item Executes a single stream of read and write requests.
	\item Executes multiple, occasionally colliding streams of read and write requests.
	\item Writes to memory data from {\tt ntsc\_capture}.
	\item Reads from memory an image to {\tt vga\_display}.
	\item Outputs to and captures data from {\tt LPF}.
	\item Captures data from {\tt projective\_transform}.
	\item Shifts data locations when {\tt ntsc\_capture} starts providing a new image.
	\item (Time permitting:) Read an image from flash memory and store in RAM for use as transformed image.
	\end{itemize}

% Jose
\item[] {\tt LPF:} applies lowpass filters, vertically and horizontally, on the image that is to be warped, in order to prevent aliasing at the output.
	\begin{itemize}
	\item (Out of time:) Just fetches pixels from memory and feeds them to {\tt projective\_transform}. LPF does not filtering.
	\item Stalls operation when fetching or writing a pair of pixels and {\tt memory\_interface} has not pulsed {\it done\_lpf}.
	\item Loads appropriate filter coefficients based on the coefficients $M_x$ and $M_y$ from {\tt object\_recognition}.
	\item Reads data from memory vertically and horizontally, and has the necessary data for the calculation of each output pixel in its buffers.
	\item Mirrors the data appropriately in its buffers when processing near an edge.
	\item Outputs to memory\_interface a pair of pixels that correspond to the convolution sum of the corresponding data.
	\end{itemize}

% Logan
\item[] {\tt ntsc\_capture}
	\begin{itemize}
	\item 1
	\item 2
	\item etc
	\end{itemize}

% Jose
\item[] {\tt vga\_display}: fetches data from memory and displays it on the screen.
	\begin{itemize}
	\item Displays a predefined pattern on the screen.
	\item Requests a pixel one video clock cycle before it is needed.
	\item Reads an image from memory, through {\tt memory\_interface}, and correctly displays it on the screen.
	\end{itemize}

\end{itemize}

\end{document}
