\documentclass[11pt]{article}
\usepackage{geometry}
\geometry{letterpaper}   
\usepackage{setspace}
\onehalfspacing
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Recursive Augmented Reality}
\author{Jos\'{e} E. Cruz Serrall\'{e}s \& Logan Williams}
\date{} 

\begin{document}
\maketitle


In our project, we will implement an augmented reality system that can overlay a digital image on video of a real world environment. We begin by reading NTSC video from a video camera and storing it in FPGA BRAM, or if more memory is required for computation, in ZBT SRAM. A picture frame with colored markers on the corners is held in front of the camera. We then perform chroma-based object recognition to recognize the corners in the video, and extract the co-ordinates that the overlayed image should be projected to. Using these co-ordinates, we apply appropriate translation, scaling, rotation, possibly skew and anti-aliasing FIR filters to an image. We then output VGA video of the original captured image, with the processed image overlayed on top of the frame. The overlayed image (the ``augmentation'') can be arbitrary. When this image is the frame of video that was previously displayed, we call the system ``recursive'', as we obtain the same image within itself. Depending on the precision of our image transformations, we could add many layers to this recursion.

\end{document}  
